Performing graph-based clustering with rOpenScPCA

### 2024-12-16 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
add some simple plots with a color i like that may not survive review

suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(Seurat)
  library(dplyr)
})
```

@@

@@

@@

@@

To demonstrate this, we'll convert our SCE object to a Seurat using the function `rOpenScPCA::sce_to_seurat()`.
We'll set `use_symbols = FALSE` to preserve Ensembl ids as the feature names rather than converting to gene symbols.
Then, we'll use a simple Seurat pipeline to obtain clusters.

```{r sce to seurat, message = FALSE}
# Convert the SCE to a Seurat object using rOpenScPCA, preserving Ensembl ids as feature names
seurat_obj <- rOpenScPCA::sce_to_seurat(sce, use_symbols = FALSE)

>>>>

suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(Seurat)
  library(dplyr)
  library(ggplot2)
})

# Set ggplot theme for plots
theme_set(theme_bw())
```

@@

We can visualize these results by plotting silhouette width across clusters as violin plots, for example:

```{r violin silhouette}
ggplot(silhouette_results) +
  aes(x = cluster, y = silhouette_width) +
  geom_violin(fill = "darkolivegreen3") +
  labs(x = "Cluster", y = "Silhouette width")
```

@@

We can visualize these results by plotting purity clusters as violin plots, for example:

```{r violin purity}
ggplot(purity_results) +
  aes(x = cluster, y = purity) +
  geom_violin(fill = "darkolivegreen3") +
  labs(x = "Cluster", y = "Neighborhood purity")
```

@@

We can visualize these results by plotting stability as a density plot, for example:

```{r ari density}
ggplot(stability_results) +
  aes(x = ari) +
  geom_density(color = "grey30", fill = "darkolivegreen3") +
  labs(x = "Adjusted rand index across bootstrap replicates")
```

@@

To demonstrate this, we'll convert our SCE object to a Seurat using the function `rOpenScPCA::sce_to_seurat()`.
Then, we'll use a simple Seurat pipeline to obtain clusters.
<!-- TODO: We will want to reference this module for further documentation on this function: https://github.com/AlexsLemonade/OpenScPCA-analysis/issues/945 -->

```{r sce to seurat, message = FALSE}
# Convert the SCE to a Seurat object using rOpenScPCA
seurat_obj <- rOpenScPCA::sce_to_seurat(sce)
